### 2018-02-28 thesis/contents/discussions.tex

The introduction of DTI in the study of TN has revolutionized our understanding of this disorder. Moving away from clinical studies alone, DTI is able to derive metrics that provide important information on the microstructure of the nerve which can then be related to specific processes such as changes in myelination or the microstructure of the axons. Thus DTI provides an important objective measure in the study of pain, which was unavailable up unto this point. The earliest work on the feasibility of accurate reconstruction of cranial nerve with DTI tractography \cite{Hodaie2010} in 2010. This study was able to image CN II, III, and importantly CN V. Similarly, we were able to establish the methods to image the TRG and the cisternal CN V with manual delineation, followed by visualization of the CN V postganglionic GK target, prior and after surgery \cite{Hodaie2012g}. We found alternations in both the CN V reconstruction, as well as FA in the surgical target location, that improved our understanding beyond what is visible with post-surgical gadolinium enhancements. This has now led our team to study whether CN V GK target diffusivity at 6 months post-surgery can predict long-term pain relief in TN \cite{Tohyama2018}. Similarly whether the diffusivity changes are specific enough that they can serve as predictors of outcome \cite{Hung2017}. The tractography study of TN has been directly linked with the study of gray and white matter abnormalities of the TN brain \cite{Desouza2013c}. The value of DTI studies in TN is therefore unique, and creates a strong context for the work done in this thesis.

>>>>

The introduction of DTI in the study of TN has revolutionized our understanding of this disorder. Moving away from clinical studies alone, DTI is able to derive metrics that provide important information on the microstructure of the nerve which can then be related to specific processes such as changes in myelination or the microstructure of the axons. Thus DTI provides an important objective measure in the study of pain, through a previously unavailable approach. The earliest work on the feasibility of accurate reconstruction of cranial nerve with DTI tractography \cite{Hodaie2010} dates to 2010. This study was able to image CN II, III, and importantly CN V. Similarly, we were able to establish the methods to image the TRG and the cisternal CN V with manual delineation, followed by visualization of the CN V postganglionic GK target, prior and after surgery \cite{Hodaie2012g}. We found alternations in both the CN V reconstruction, as well as FA in the surgical target location, that improved our understanding beyond what is visible with post-surgical gadolinium enhancements. This has now led our team to study whether CN V GK target diffusivity at 6 months post-surgery can predict long-term pain relief in TN \cite{Tohyama2018}. Similarly whether the diffusivity changes are specific enough that they can serve as predictors of outcome \cite{Hung2017}. The tractography study of TN has been directly linked with the study of gray and white matter abnormalities of the TN brain \cite{Desouza2013c}. The value of DTI studies in TN is therefore unique, and creates a strong context for the work done in this thesis.

### 2018-02-28 thesis/contents/reviews/dmri.tex
Updates from ShareLaTeX

\begin{figure}[ht]
\begin{center}
\begin{tabular}{c}
\includegraphics[width=3.5in]{diffusion.pdf}
\end{tabular}
\caption{Isotropic diffusion: diffusion of molecules have the same probable displacement in all directions. Anisotropic diffusion displacement of modules are constrained to its diffusion medium.}
\label{fig:diffusion}
\end{center}
\end{figure}

@@

FA has been found to correlate with a wide spectrum of neuromorphological changes, including but not limited to multiple sclerosis \cite{Cercignani2001,Ciccarelli2003d,Miron2012}, vestibular schwannomas \cite{Chen2011b,Taoka2006,Wai2009}, tumors \cite{Mori2002,Schonberg2006,Nimsky2005}, schizophrenia \cite{Rametti2009,Fitzsimmons2009}, traumatic brain injury \cite{Bendlin2008,Kinnunen2011c,Hellyer2012}. RD is found to positively correlate with degree of demyelination in multiple sclerosis \cite{Song2005,Song2002,Klawiter2011,Janve2013}, and well as stages of white-matter development and aging \cite{Counsell2006,Sala2010}, including alzheimer's disease \cite{Acosta-Cabronero2012}. AD is correlated positively with axonal integrity \cite{Song2003}, and is found to be a correlate of axonal injury \cite{Budde2009} such as those found in traumatic brain injury \cite{Kinnunen2011c} and Gulf War illness \cite{Rayhan2013}. MD is correlated with tissue inflammation and edema \cite{Senda2012g}, and is found to correlate with diffusivity changes as a result of gliomas \cite{Stadlbauer2007}, multiple sclerosis \cite{Cercignani2001,Senda2012g,DeGroot2013}, amyotrophic lateral sclerosis \cite{Sharma2012}, and aging \cite{Kantarci2011}.

@@

\begin{figure}[ht]
\begin{center}
\begin{tabular}{c}
\includegraphics[width=100mm]{harmonics.pdf}
\end{tabular}
\caption{Visualization of the spherical harmonic functions up to l=3.}
\label{fig:harmonics}
\end{center}
\end{figure}

>>>>

\begin{figure}[ht]
\begin{center}
\begin{tabular}{c}
\includegraphics[width=0.8\textwidth]{diffusion.pdf}
\end{tabular}
\caption{Isotropic diffusion: diffusion of molecules have the same probable displacement in all directions. Anisotropic diffusion displacement of modules are constrained to its diffusion medium.}
\label{fig:diffusion}
\end{center}
\end{figure}

@@

FA has been found to correlate with a wide spectrum of neuromorphological changes, including but not limited to multiple sclerosis \shortcite{Cercignani2001,Ciccarelli2003d,Miron2012}, vestibular schwannomas \shortcite{Chen2011b,Taoka2006,Wai2009}, tumors \shortcite{Mori2002,Schonberg2006,Nimsky2005}, schizophrenia \shortcite{Rametti2009,Fitzsimmons2009}, traumatic brain injury \shortcite{Bendlin2008,Kinnunen2011c,Hellyer2012}. RD is found to positively correlate with degree of demyelination in multiple sclerosis \shortcite{Song2005,Song2002,Klawiter2011,Janve2013}, and well as stages of white-matter development and aging \shortcite{Counsell2006,Sala2010}, including alzheimer's disease \shortcite{Acosta-Cabronero2012}. AD is correlated positively with axonal integrity \shortcite{Song2003}, and is found to be a correlate of axonal injury \shortcite{Budde2009} such as those found in traumatic brain injury \shortcite{Kinnunen2011c} and Gulf War illness \shortcite{Rayhan2013}. MD is correlated with tissue inflammation and edema \shortcite{Senda2012g}, and is found to correlate with diffusivity changes as a result of gliomas \shortcite{Stadlbauer2007}, multiple sclerosis \shortcite{Cercignani2001,Senda2012g,DeGroot2013}, amyotrophic lateral sclerosis \shortcite{Sharma2012}, and aging \shortcite{Kantarci2011}.

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=\textwidth]{harmonics.pdf}
\caption{Visualization of the spherical harmonic functions up to l=3. Modified from \protect\cite{sh-image-wikipedia}}
\label{fig:harmonics}
\end{center}
\end{figure}
